Forward Modeling Galaxy Size in a Cosmological Context

### 2017-10-04 paper/galsize_paper.tex
Previous work section is done once somerville discussion is complete

Our approach is closely aligned with the methods used in \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\langle\rhalf\vert\mstar\rangle$ relation.

\ben
\item \citet{cebrian_trujillo14} - NYU-VAGC find that field galaxies are slightly larger than high-density regions (defined by 2Mpc smoothing kernel)
\een

>>>>

Our approach is closely aligned with the methods used in \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\langle\rhalf\vert\mstar\rangle$ relation. By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, the authors in \citet{somerville_etal17} found that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies. Since the latter necessarily receives an additional contribution from measurement error, this implies some tension with the common semi-analytic modeling assumption that $\lambda_{\rm halo}$ scales with $\rhalf.$ As noted in \citet{somerville_etal17}, this evidence cannot be used to directly test the $\lambda_{\rm halo}\propto\rhalf$ assumption because the physical motivation for this correlation is largely limited to disk galaxies \citep{mo_mao_white98}.
